\pagestyle{empty}% Set page style to empty
\pdfbookmark[0]{Acknowledgements}{Acknowledgements} % Bookmark name visible in a PDF viewer
\begin{center}
	\Huge \textsc{\textbf{Acknowledgements}}
	\hrulefill
\end{center}
The writing of this section has been a rather emotional time as it's made me retrace my entire PhD journey.

Since I've started the programme, my supervisor, Fabrizio Salvatore, has constantly been an outstanding support across the whole spectrum of my needs, as a PhD student. Not only has he been able to spot in advance when I needed support, no matter whether work-related or simply the right joke at the right time that would cheer me up, but he's also been to me a warm human being equipped with a distinguished dose of both empathy and motivation capability. My second supervisor and head of the \textsc{ATLAS}-Sussex group, Antonella De Santo, has also been a constant presence to whom I feel grateful for the support provided and with whom I shared all my PhD-related moans. 
%among all my PhD-related moans, an exhausting 8-hour train trip from Sheffield, back to Brighton after the IOP Conference in 2017. 
I feel grateful also to Iacopo Vivarelli and Alex Cerri whose doors have always been open, whenever I had questions or doubts. Thanks Alex for all the delicious dinners at yours, which you've sweetened my \textsc{LTA} at \textsc{CERN} with. Thanks also to you, Lily, for the great \emph{\#ScienceOnBuses} project you've organised and for the amazing times, even if just few, we've spent at the pub. In other words, my experience at Sussex has been just wonderful. The perfect chance for a professional and personal growth.

A few people properly mentored me throughout the whole programme. Kerim Suruliz, Mark Sutton, and Zara Grout, who's since moved on from the group, are unquestionably the people who've shared their knowledge with me the most (besides the outrageous number of lines of code). Without you guys, it would've been a nightmare. Nicky, Carlos, and Umberto, who've also since moved on from the group, and Benedict, have always been a friendly presence, at both Sussex and \textsc{CERN}, and also outside the work environment.

Yusufu Shehu, a.k.a. \emph{Suf}, has played a major role across my whole PhD. He's taken me by the hand through the difficulties that one has to go through when approaching the \textsc{ATLAS} world, but he's especially been the one who's helped me the most with the traumatising transition that a Sicilian guy has to face when moving to a country like the UK (language, culture, etc.). Thanks Suf. Not only have you been a great colleague, but you've also become a great friend who I've shared sad times, emotional outbursts, and nights out in Brighton with, along the line of \emph{Tales of ordinary madness}. 

A big \emph{Thank you!} goes also to Giuseppe Lerner who, with his remarkable generosity and physics knowledge, has helped me go through the sourness of the last 4 years, and who I've shared pints, laughter, and interesting discussions with. To people like Mark Stringer, James Waterfield, and Ed Leming, I would like to say: \emph{``Thanks lads. My time here wouldn't have been the same without you''}.

I'd also like to thank Nicola, Sam, Emma, Tom, electroweak Fab, Giovannis and the Marios, who've been a good company to share the office with, and Jack and Rob for having shared the pain of living in a crappy house. Special thanks to Fabione and Vangelis, who've not only been good physicists to share thoughts with, but trips and drinks, too.

When it comes to my \textsc{LTA} period at \textsc{CERN}, Benjamin Sowden and Callum Kilby are the ones who I'd like to mention. They've been great officemates who've provided me with a lot of incredibly useful insights about the life at \textsc{CERN} (and lines of code), and who I've shared my times in \textsc{R1} with. Thanks also to STFC for the funding provided. And how could I not mention Massimo, Mario, and Daniele?! You've all been social-life saviours with joyful dinners at mine and nights out in Geneva. Thank you! 

Among the \textsc{ATLAS} $\stop0\ell$ group members I would like to thank Andrea Rodriguez and Walter Hopkins who've been a pleasure to work with. Your friendly attitude has helped me get the work done and ease the stress of endless boring \emph{cutflow challenges}.\\\emph{Two (three) in distress make sorrow less}.

An expression of sincere gratitude goes to my MSc supervisor, Giuseppe Verde, who's made me want to go for a PhD, who's given me the boost of confidence I needed, and whose help has also been decisive to get where I am now. 

To all of you my Sicilian mates, particularly to you Lucìgno, inspiring, reliable, eternally funny friend, ready to listen and solve my problems, and to all those spread across the globe, to you Massimo and Renatano, always there no matter what, to you Scifo, Enza, Emilianottide, Sebi, to you Gesu, Michi, Stefano, Curenti, Barbone, Amenta, to you Pietro and Pistocchi, friends of a lifetime, to all of you lovely pack of kooks, I save a special place in my heart. You've been managing to make up for the distance that separates us with either fantastic reunions, or long Play Station sessions during those stay-at-home weekends. You've always been a constant and pleasant presence even if thousands of miles away from me.

To my family, a continuous warmth dispenser, a safety net that has been giving me the strength not to give up even during the toughest times, a huge \emph{thank you} for having been a financial support throughout my education and the backbone of my entire upbringing. The credits of what I've become go to you Dad, to you Mum, and to you Sister. This work's also for you, it's for us.

Finally, my last thought is for you Martina. Your patience, support, and affection, helped me deal with the last tough years more than anything else. I hope the best has yet to come.